Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
rev

@@

\begin{frame}{ML-Like: Path-Dependent Types}
\begin{itemize}
\item Scala's abstract types  $\approx$ ML's abstract types of signatures; limitations:
\begin{itemize}
\item recursive references
\item bounded quantifications
\end{itemize}
\item translucent sum can be given a more precise type by referring to the name of its member path with a path selection; essential for
\begin{itemize}
\item breaking the dependencies between (sub)fields
\item propagation of typing information
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\begin{frame}{ML-Like: Calculus}
grounded in type theory; based on Girard's $F_\omega$, adding:
\begin{itemize}
\item {\it translucent sums} to model modules
\item dependent functions to model functors
\item a notion of subtyping to model module implementation-interface matching
\end{itemize}
\end{frame}

@@

\begin{frame}{ML-Like: Path-Dependent Types}
\begin{itemize}
\item Scala's abstract types  $\approx$ ML's abstract types of signatures; limitations:
\begin{itemize}
\item recursive references
\item bounded quantifications
\end{itemize}
\item translucent sum can be given a more precise type by referring to the name of its type member with a path selection; essential for
\begin{itemize}
\item breaking the dependencies between (sub)fields
\item propagation of typing information
\end{itemize}
\end{itemize}
\end{frame}
